\documentclass[twocolumn,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\author{Josh Pattman}
\title{Evolutionary Learning In Grouped Gene Networks}
\begin{document}
	\maketitle
    \section{Introduction 1.5PM}
    Introduction: You need not spend more than 1.5 pages describing the original paper.
    \begin{itemize}
        \item The displayed genes of a creature, their phenotype, is not only influenced by their own genetic code, know as their genotype, but also through complex interactions between the genes of that creature.
        \item This means that each trait displayed by a creature is actually the result of the entire genotype, and not just a single locus in the genetic code.
    \end{itemize}

    \section{Experiment Setup}
    \begin{itemize}
        \item What you evolved including:
        \item \begin{itemize}
            \item How you represented individuals
            \item What fitness function did you define
            \item What kind of GA you used
            \item Steady state/ generational?  Tournament selection/ fitness proportionate (roulette wheel)?
            \item What kind of crossover (if any) you used.
            \item All parameters (enough detail so a reader could re-implement the GA)
        \end{itemize}
    \end{itemize}

    \section{Reimplemented Results}
    \begin{itemize}
        \item 1 Page
        \item The reimplemented figures (side by side with the originals)
        \item Discussion of what the results show/don't show, what worked/didn't work, what you learned
    \end{itemize}


    \section{Extension}
    \begin{itemize}
        \item 1 Page
        \item What is your research question/hypothesis?
        \item \begin{itemize}
            \item e.g., 'compare x with y' or 'add x and see what difference it makes compared to not(x)'.
        \end{itemize}
        \item Describe methods / any advancements
        \item Support the value of asking that question (using literature)
        \item What do you expect to happen (what might happen)?
        \item Why do you think that?
    \end{itemize}


    \section{Extension Results}
    \begin{itemize}
        \item 1.5 page
    \end{itemize}


    \section{Conclusion}
    \begin{itemize}
        \item one page
        \item What do you conclude from that
        \item significance of the extension results
        \item critique/evaluation
    \end{itemize}


    \section{Appendix}


\end{document}